\begin{frontmatter}

%% Title, authors and addresses

%% use the tnoteref command within \title for footnotes;
%% use the tnotetext command for the associated footnote;
%% use the fnref command within \author or \address for footnotes;
%% use the fntext command for the associated footnote;
%% use the corref command within \author for corresponding author footnotes;
%% use the cortext command for the associated footnote;
%% use the ead command for the email address,
%% and the form \ead[url] for the home page:
%%
%% \title{Title\tnoteref{label1}}
%% \tnotetext[label1]{}
%% \author{Name\corref{cor1}\fnref{label2}}
%% \ead{email address}
%% \ead[url]{home page}
%% \fntext[label2]{}
%% \cortext[cor1]{}
%% \address{Address\fnref{label3}}
%% \fntext[label3]{}

%\title{A survey of Computer-Aided Detection and Diagnosis systems for prostate cancer diagnosis based on mono and multi MRI/MRSI modalities}
\title{Computer-Aided Detection and Diagnosis for prostate cancer based on mono and multi-parametric MRI: A review}

%% use optional labels to link authors explicitly to addresses:
%% \author[label1,label2]{<author name>}
%% \address[label1]{<address>}
%% \address[label2]{<address>}

\author[label1,label3]{Guillaume~Lema\^itre\corref{cor1}}
\ead{guillaume.lemaitre@udg.edu}
\author[label3]{Robert~Mart\'i}
\ead{marly@eia.udg.edu}
\author[label3]{Jordi~Freixenet}
\ead{jordif@eia.udg.edu}
\author[label4]{Joan~C.~Vilanova}
\author[label2]{Paul~M.~Walker}
\ead{pwalker@u-bourgogne.fr}
\author[label1]{Fabrice~Meriaudeau}
\ead{fabrice.meriaudeau@u-bourgogne.fr}


\address[label1]{\scriptsize LE2I-UMR CNRS 6306, Universit\'{e} de Bourgogne, 12 rue de la Fonderie, 71200 Le Creusot, France}
\address[label2]{\scriptsize LE2I-UMR CNRS 6306, Universit\'{e} de Bourgogne, Avenue Alain Savary, 21000 Dijon, France}
\address[label3]{\scriptsize ViCOROB, Universitat de Girona, Campus Montilivi, Edifici P4, 17071 Girona, Spain}
\address[label4]{\scriptsize Department of Magnetic Resonance, Cl\'inica Girona, Lorenzana 36, 17002 Girona, Spain}

\cortext[cor1]{Corresponding author.}

\begin{abstract}
Prostate cancer is the second most diagnosed cancer of men all over the world. In the last decades, new imaging techniques based on Magnetic Resonance Imaging (MRI) have been developed improving diagnosis. In practise, diagnosis can be affected by multiple factors such as observer variability and visibility and complexity of the lesions. In this regard, computer-aided detection and computer-aided diagnosis systems have been designed to help radiologists in their clinical practice. Research on computer-aided systems specifically focused for prostate cancer is a young technology and has been part of a dynamic field of research for the last ten years. This survey aims to provide a comprehensive review of the state of the art in this lapse of time, focusing on the different stages composing the work-flow of a computer-aided system. We also provide a comparison between studies and a discussion about the potential avenues for future research. In addition, this paper presents a new public online dataset which is made available to the research community with the aim of providing a common evaluation framework to overcome some of the current limitations identified in this survey.
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
computer-aided detection \sep computer-aided diagnosis \sep prostate cancer \sep magnetic resonance imaging \sep magnetic resonance spectroscopy imaging \sep computer vision 
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)

\end{keyword}

\end{frontmatter}
